When does vapor pressure deficit drive or reduce evapotranspiration?

### 2019-02-17 doc/paper/body.tex
tables look good but untested within latex

\begin{table}
  \caption{Plant functional types, their abbreviation, calculated
    Medlyn coefficient, and calculated uWUE. uWUE from
    \citet{Zhou_2015}, including the observed standard deviation, is
    shown for comparison. Note that uWUE from \citet{Zhou_2015} is
    calculated from a different set of sites, and that units are
    converted such that the quantities work with Equations 1-8 and the
    variables defined Table \ref{definitions}.}
  \small
  \label{pft}
  \centering
  \begin{tabular}{l c c @{\qquad} c c}
    \hline
    \multirow{2}[3]{*}{Abbreviation} & \multirow{2}[3]{*}{PFT} & \multirow{2}[3]{*}{$g_1$ (Pa$^{0.5}$)} & \multicolumn{2}{c}{uWUE ($\mu$-mol [C] Pa$^{0.5}$ J$^{-1}$ [ET])}  \\
    \cmidrule{4-5}

                                     & & & fitted & \citet{Zhou_2015} \\

@@

In the ``sign term'' most of quantities are relatively constant,
except for VPD and the plant parameters g$_1$ and uWUE. In the scaling
term, most of the terms are relatively constant with the exception of
aerodynamic conductance ($g_a$) and temperature (especially its effect
on $\Delta$). To determine the range of probable ET reponses to VPD we
will systematically vary this parameters according to Table
\ref{param_values}. Environmental parameters ($g_a$, $T$) are varied
according to ranges we would expect for growing season conditions
across a range of plant types (canopy height is a determinant $g_a$),
and plant parameters (g$_1$, uWUE) are varied according to ranges
established in previous literature \citep{Zhou_2015,
  Medlyn_2017}. Using this previous literature we can connect the
effect of varying plant parameters to specific plant types and
characteristics. Lastly, all code and data used in this analysis,
including those used to generate the figures and tables, are publicly
available at \url{https://github.com/massma/climate\_et}.
%\hyperref[https://github.com/massma/climate\_et]{https://github.com/massma/climate_et}.

>>>>

\begin{table}
  \caption{Plant functional types, their abbreviation, calculated
    Medlyn coefficient, and calculated uWUE. uWUE from
    \citet{Zhou_2015}, including the observed standard deviation, is
    shown for comparison. Note that uWUE from \citet{Zhou_2015} is
    calculated from a different set of sites, and that units are
    converted such that the quantities work with Equations 1-8 and the
    variables defined Table \ref{definitions}. }
  \small
  \label{pft}
  \centering
  \begin{tabular}{l c c c}
    \hline
    Symbol & min (~15th percentile) & med (~50th percentile ) & max
                                                                (~15th
                                                                percentile)
    & citation

@@

In the ``sign term'' most of quantities are relatively constant,
except for VPD and the plant parameters g$_1$ and uWUE. In the scaling
term, most of the terms are relatively constant with the exception of
aerodynamic conductance ($g_a$) and temperature (especially its effect
on $\Delta$). To determine the range of probable ET reponses to VPD we
will systematically vary this parameters according to Table
\ref{param_varying}, while all other parametrs are held fixed (Table
\ref{param_fixed}). Physical variables ($g_a$, $T$) and plant
physiological paramters (g$_1$, uWUE) are varied according to
literature-based expectations for a range of growing season conditions
and plant types \citep{Zhou_2015, Medlyn_2017}. Using this previous
literature we can connect the effect of varying plant parameters to
specific plant types and characteristics. Lastly, all code and data
used in this analysis, including those used to generate the figures
and tables, are publicly available at \url{https://github.com/massma/climate\_et}.
%\hyperref[https://github.com/massma/climate\_et]{https://github.com/massma/climate_et}.

\begin{table}
  \caption{Variable quantities in the ET response to VPD. Each value
    is varied to determine the effect of a range of expected plant and
    environmental conditions on ET response to VPD. A citation is
    provided in cases where the quantites are directly derived from
    previous literature. Conceptual percentiles
    for interpreting each quantity are noted.}
  \label{param_varying}
  \centering
  \begin{tabular}{l c c c c c}
    \hline
    Symbol & units [units in citation] & min (~15th percentile) & med (~50th percentile) & max
                                                                                            (~15th
                                                                                            percentile)
    & citation  \\
    \hline
    \input{param_varying.tex}
    \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Quantities that are fixed in the ET response to VPD
    (relative to those in Table \ref{param_varying}).}
  \label{param_varying}
  \centering
  \begin{tabular}{l c c}
    \hline
    Symbol & units & value \\
    \hline
    \input{param_fixed.tex}
    \hline
  \end{tabular}
\end{table}
